Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-29 journal/article.tex
Work in progress: Coaching

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Pilot programs and other piloting   & 
                P6-P11, P14, P16, P18, P22, P23, P24, P27, P29,
                P36, P38, P40, P41, P43, P45, P46, P47  \\  %22
        \bottomrule
    \end{tabular}
    \caption{Summary of activities aiming to advance the transformation}
    \label{table:transformation_activities}
\end{table}

@@

% Some training included simulation workshops [P40, P41].
% Hands-on workshops [P46].

@@

@@

@@

>>>>

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1, P2, P3, P6, P8, P9, P16, P18, P23, P27, P29,
                P33, P36, P39, P40, P41, P45, P46, P47, P50, P52  \\  % 21
        Pilot programs and other piloting   & 
                P6-P11, P14, P16, P18, P22, P23, P24, P27, P29,
                P36, P38, P40, P41, P43, P45, P46, P47  \\  % 22
        \bottomrule
    \end{tabular}
    \caption{Summary of activities aiming to advance the transformation}
    \label{table:transformation_activities}
\end{table}

@@

% Some training included simulation workshops [P40, P41].
% Hands-on workshops [P46]. 
% Certified Scrum master training --> In several cases

@@

% Coaching

Why is coaching used?

Coaches are who?

Who receives coaching --> Teams, very few cases with some other roles

How is coaching done?

@@

Coaches were driving the agile push [P2].

Coaching was considered very important at project start. Otherwise there may be
severe long term consequences [P8].

Coaching was also seen as an important success factor [P29, P33].

The agile adoption erquired coaches [P47].

Internal coaches were required for making the change grow [P47].

To be able to coach efficiently it was required that the coach had detailed
understanding of the company's processes and systems [P23]

Coaches were also involved in training [P27].

Scrum masters that had been trained earlier were coaching the teams in some
cases.

@@

[P1, P2]
* Why: best for introducing agile methods
* Why: They drive the push
* How: Coach in the team

[P3]
* Why: The change leader persuaded to introduce coaching
* Coach: The change leader
* Who: teams
* How: Teams were coached

[P6]
* Why: It helps to have people with experience
* Coach: An internal change leader, a team of coaches
* Who: Teams
* How: Start heavy a kick-off, and later draw back
* Particular: There were little coaches at start
* Particular: The coaches showed positive results, and management was convinced to invest in coaching

[P8]
* Why: Intensive coaching is necessary 4-6 months at start

[P9]
* Coach: A hired consultant specialist
* How: The coach embodied the best agile principles

[P16]
* Why: To ensure trainsformation is successful
* Coach: The cross-functional rollout team

[P18]
* Coach: An agile consultant
* When: For over a year
* How: Accompanied the introduction for over a year, trained on specific agile practices

[P23]
* Coaches: In-house coaching team, some external coaches
* The coach community needed to be tended to specifically
* If there were too few coaches things did not work
* Pair coaching, apprentice coaching
* Particular: The coaches needed to have specific knowledge of the company's systems and processes
* Particular: Coaches in pairs --> training of coaches
* Particular: Focus on coaching

[P27]
* Coaches: External coaches
* How: Train on agile practices

[P29]
* Coaches: Agile consultants
* Why: Having a impartial third party was a key success factor
--
* Coaches: The pilot team, matured teams
* Who: Teams
* How: Helping other teams in getting started
* How: Taking a formal mentoring role when it is required

[P33]
* Who: Product owners
* Why: Crucial to make it successful
* Particular: Coaches were brought in after the start of the transformation, when trouble already existed

[P36]
* Coaches: Coaches from a subcontractor
* How: The coached drive the project
* How: Mentor in-house leads to take lead as soon as possible
* How: Retrospect and adapt
* When: The need for coaches disappeared gradually
* The coach role was apparently seen as the lead of the project

[P39]
* Coach: External support, hired Chief Scrum masters
* How: inspect and adapt

[P40]
* Who: Teams
* How: Coaching breakout sessions

[P41]
* Coach: Internal and external
* Who: Teams
* How: Coaching office hours
* How: Have a forum where teams can ask for help, and to share their implementation
* Particular: It was disliked to have peers as coaches, as they were not considered more knowledgeable

[P45]
* Coach: Internal small expert team
* Who: Teams
* How: Supporting, advocating agile development
* How: Educate and support teams interested in Scrum
* Particular: Later offering possibility to teach more Scrum mentors

[P46]
* The pilot teams were coached
* Who: Teams that are about to start agile projects
* How: A productized training workshop, and a jump start afterwards
* How: Key team roles are coached in the start, so that the start is successful

[P47]
* Why: The agile adoption required coaches
* Coaches: Initially external consultants
* Coaches: Internal people started taking coach positions
* Coaches: Apprentice coaches, guided by external experts
* Particular: A structure was created around coach certification
* Particular: A coach community

[P50]
* Coaches: Internal key roles, these received initial coach and role specific training
* When: When teams were starting
* How: Coached to facilitate start up of teams

[P52]
* Who: Paired line manager and Scrum master
* How: Pair coaching the pair itself
* Coach: In some cases an experienced Scrum master was brought to help the pair
